---
title: "SAR9_21"
author: "Qingyu Luo,Junxiao Li,Jiawen Wang,Chaozhuo Hua"
date: "2022/9/24"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

Import necessary files and packages.

```{r setup,include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
source("../../Code/R/imagematrix.R")
```

# K and G0 distributions

## Probability density function of k distribution & random generator

$$
\mathrm{f}_{\mathrm{Z}}(z ; \alpha, \lambda, \mathrm{L})=\frac{2 \lambda \mathrm{L}}{\Gamma(\alpha) \Gamma(\mathrm{L})}(\lambda \mathrm{Lz})^{\frac{\alpha+\mathrm{L}}{2}-1} \mathrm{~K}_{\alpha-\mathrm{L}}(2 \sqrt{\lambda \mathrm{Lz}}) \mathbb{1}_{\mathbb{R}_{+}}(z)
$$

```{r}
dKI <- function(z, p_alpha, p_lambda, p_Looks, log=FALSE) {
  
  if(log==FALSE) {
    
    lLz <- p_lambda * p_Looks* z
    
    return((2*p_lambda*p_Looks/(gamma(p_alpha)*gamma(p_Looks))) *
             (lLz)^((p_alpha+p_Looks)/2-1) *
             besselK(x = 2*sqrt(lLz), nu = p_alpha-p_Looks)
    )
  }
  
}
rKI <- function(n, p_alpha,p_lambda, p_Looks) {
  
  return(
    rgamma(n, 1, p_Looks)*rgamma(n, p_alpha/p_lambda, p_alpha)
  )
  
}
```

## Probability density function of G0 distribution & random generator

$$
\mathrm{f}_{\mathrm{Z}}(z ; \alpha, \gamma, \mathrm{L})=\frac{\mathrm{L}^{\mathrm{L}} \Gamma(\mathrm{L}-\alpha)}{\gamma^\alpha \Gamma(\mathrm{L}) \Gamma(-\alpha)} \frac{z^{\mathrm{L}-1}}{(\gamma+\mathrm{Lz})^{\mathrm{L}-\alpha}}
$$

```{r}
dGI0 <- function(z, p_alpha, p_gamma, p_Looks, log=FALSE) {
  
  if(log==TRUE) {
    return(
      (p_Looks*log(p_Looks) + lgamma(p_Looks-p_alpha) + (p_Looks-1)*log(z) ) - 
        (p_alpha*log(p_gamma) + lgamma(-p_alpha) + lgamma(p_Looks) + 
        (p_Looks-p_alpha)*log(p_gamma + z*p_Looks) ) 
      )   
    }
  else { return( 
    ( p_Looks^p_Looks * gamma(p_Looks-p_alpha) * z^(p_Looks-1) ) / 
    (p_gamma^p_alpha * gamma(-p_alpha) * gamma(p_Looks) * (p_gamma + z*p_Looks)^(p_Looks-p_alpha)) 
  )
  }
}
rGI0 <- function(n, p_alpha, p_gamma, p_Looks) {
  
  return(
    rgamma(n, 1, p_Looks) / rgamma(n, -p_alpha, p_gamma)
  )
  
}
```

# Illustration of the K, G0 and Gamma distributions

## density of a K distribution

```{r fig.align = "center",fig.cap="K distribution"}
s <- seq(0.001, 10, length.out = 500)
s <- data.frame(s)
ggplot(data=s, aes(x=s),
       y=Transformations, 
       color=Transformation) +
  stat_function(fun=dKI, geom = "line", size=2, col="red", args = list(p_alpha=6, p_lambda=6, p_Looks=6)) +
  xlab("x") + 
  ylab("y") +
  labs(title = "K Distribution") +
  scale_x_log10()
```

## density of a G0 distribution

```{r fig.align = "center",fig.cap='G0 distribution'}

ggplot(data=s, aes(x=s)) +
  stat_function(fun=dGI0, geom = "line", size=2, col="blue", args = list(p_alpha=-6, p_gamma=6, p_Looks=6)) +
  xlab("x") + 
  ylab("y") +
  labs(title = "G0 Distribution") +
  scale_x_log10()
```

## histogram and density of a K distribution

```{r fig.align='center'}
p_alpha=6
p_lambda=6
p_Looks=6
pk_num=50000
s <- rKI(pk_num, p_alpha, p_lambda, p_Looks) 
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="yellow",color="black",bins=nclass.FD(unlist(s))/10) +
  geom_density(col="red", size=1) +
  geom_boxplot(aes(y=1), width=.1)+
  stat_ecdf(col="blue") +
  xlab("x") +
  ylab("y") +
  labs(title="histogram & density") +
  scale_x_log10()
```

## histogram and density of a G0 distribution

```{r G0 distribution random generator,fig.align='center',fig.cap='random number generators for G0 distribution'}
p_alpha=-6
p_gamma=6 
p_Looks=6
pG0_num=50000
s <- rGI0(pG0_num,p_alpha, p_gamma, p_Looks)
s <- data.frame(s)
ggplot(data = s, aes(x=s)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="yellow",color="black",bins=nclass.FD(unlist(s))/10) +
  geom_density(col="red", size=1) +
  geom_boxplot(aes(y=1), width=.1)+
  stat_ecdf(col="blue") +
  xlab("x") +
  ylab("y") +
  labs(title = "Histogram & smoothed histogram") +
  scale_x_log10()
```

## density of a dgamma distribution.

```{r fig.align = "center"}
s <- seq(0.001, 10, length.out = 500)
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="red", args = list(shape=6, scale=1/6)) +

  xlab("x") + 
  ylab("y") +
  labs(title = "dgamma Distribution") +
  scale_x_log10()
```

## histogram of a dgamma distribution.

```{r fig.align='center'}
s <- seq(0.01, 10, length.out = 500)
dg <- dgamma(s,6,1/6)
dg <- data.frame(dg)
ggplot(data=dg, aes(x=s)) +
  geom_histogram(aes(y=..density..),
                 bins=80,
                 col="black", fill="white")+
  xlab('x')+
  ylab("density")
```

## density of a pgamma distribution.

```{r fig.align = "center"}
s <- seq(0.001, 10, length.out = 500)
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  stat_function(fun=pgamma, geom = "line", size=2, col="red", args = list(shape=6, scale=1/6)) +
  xlab("x") + 
  ylab("y")
```

## histogram of a pgamma distribution.

```{r fig.align='center'}
s <- seq(0.01, 10, length.out = 500)
dg <- pgamma(s,6,1/6)
dg <- data.frame(dg)
ggplot(data=dg, aes(x=s)) +
  geom_histogram(aes(y=..density..),
                 bins=80,
                 col="black", fill="white") +
  xlab('x')+
  ylab("density")
```

# Analysis of the bright image data

```{r include=FALSE}
load("../../Data/Rdata/bright.Rdata")
```

General Information of the dataset. From the information below, we can see the dataset is a 3-d tensor, containing 3x109x214 elements.

```{r}
dim(bright)
typeof(bright)
range(bright)
bright_data <- data.frame(bright=as.vector(bright))
summary(bright_data)
```

Set x to uniform scale and semilog scale, and plot the dataset separately.

```{r fig.subcap=c('Linear scale', 'Semilogarithmic scale'),fig.align = "center"}
ggplot(bright_data, aes(x=(bright))) +
  geom_boxplot(notch = TRUE)+
  geom_boxplot(outlier.colour="red", outlier.shape=21,outlier.size=1)+
  ggtitle("plot of the dataset(uniform scale)")+
  ylab("Boxplot")
ggplot(bright_data, aes(x=bright)) +
  geom_boxplot(notch = TRUE) +
  geom_boxplot(outlier.colour="red", outlier.shape=21,outlier.size=1)+
  scale_x_log10()+
  ylab("Boxplot") +
  ggtitle("plot of the dataset(semilog scale)")
```
It can be guessed from the histogram that the data obey lognormal distribution.

```{r fig.align='center'}
ggplot(bright_data, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(bright_data)),
                 col="black", fill="white") +
  scale_x_log10()+
  xlab("Intensity in semilog scale")+
  ylab("Density") +
  ggtitle("Histogram of the dataset")
```
Use q-q plot to visualize the data to further verify the hypothesis.
```{r}
bright_log = log(bright)
qqnorm(bright_log)
qqline(bright_log)
```
Generating an image using the "imagematrix" library.
```{r Image,fig.align='center'}
plot(imagematrix(normalize(bright)))
```

```{r}
ymax <- 255
ymin <- 0
xmax <- max(bright)
xmin <- min(bright)
visual_bright = ((ymax-ymin)*(bright-xmin)/(xmax-xmin)+ymin)
```
Map the data to [0, 255] and plot again.
```{r}
plot(imagematrix(visual_bright))
```



